Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-07 paper/background.tex
Paper update

We handle the scenarios where the topology of the analog circuit is fixed, this
is practical as there are usually a lot of classical topologies for given
design task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is automatically searching for the optimal
design parameters, the problem can then be formulated as a bound-constrained
black-box optimization problem:

\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x})
\end{equation}

where $\bm{x} \in \textrm{D}$ is the vector of design variables,
$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
specifications. Given the design parameters $\bm{x}$, the FOM value can be
obtained by commercial circuit simulators like HSPICE or spectre.

@@

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution 
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x}))
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x})
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty.

@@

The LCB function is defined as follows:
\begin{equation}
    \label{eq:LCB}
    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x})
\end{equation}
Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.

>>>>

We handle the scenarios where the topology of the analog circuit is fixed, this
is practical as there are usually a lot of classical topologies for given
design task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is automatically searching for the optimal
design parameters, the problem can then be formulated as a bound-constrained
black-box optimization problem:
\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x}), 
\end{equation}
where $\bm{x} \in \textrm{D}$ is the vector of design variables,
$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
specifications. Given the design parameters $\bm{x}$, the FOM value can be
obtained by commercial circuit simulators like HSPICE or spectre.

@@

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution 
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x}))
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x}), 
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty.

@@

The LCB function is defined as follows:
\begin{equation}
    \label{eq:LCB}
    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x}), 
\end{equation}
where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.
